### 2016-07-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added page numbers to hose stream report

\vspace*{2\baselineskip}
June 2016}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2015) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

>>>>

\vspace*{2\baselineskip}
July 2016}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (July 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }
